---
title: "FARS functions"
author: "Kirill Efremov"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The package contains functions for working with [(FARS)](http://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)) data
Store data on your working directory


# Read FARS data
Reads data into data.frame from working directory. 
.csv file should be already downloaded or error message will throw out
## Parametrs
filename - Integer or string name of file for reading
## Example
fars_read("accident_2015.csv.bz2")
## Code
```{r fars_read, eval=FALSE}
  fars_read <- function(filename) {
  if(!file.exists(filename))
    stop("file '", filename, "' does not exist")
  data <- suppressMessages({
    readr::read_csv(filename, progress = FALSE)
  })
  dplyr::tbl_df(data)
}

```


# Function for ploting data of accidents in specific state and year

## Description
Takes state number and yeasr and make plot with map. If there are no state throw message "invalid STATE number: "
If there no accidents show message "no accidents to plot"

## Code
```{r fars_map_state, eval = FALSE}
  
  fars_map_state <- function(state.num, year) {
    filename <- make_filename(year)
    data <- fars_read(filename)
    state.num <- as.integer(state.num)
  
    if(!(state.num %in% unique(data$STATE)))
      stop("invalid STATE number: ", state.num)
    data.sub <- dplyr::filter(data, STATE == state.num)
    if(nrow(data.sub) == 0L) {
      message("no accidents to plot")
      return(invisible(NULL))
    }
    is.na(data.sub$LONGITUD) <- data.sub$LONGITUD > 900
    is.na(data.sub$LATITUDE) <- data.sub$LATITUDE > 90
    with(data.sub, {
      maps::map("state", ylim = range(LATITUDE, na.rm = TRUE),
                xlim = range(LONGITUD, na.rm = TRUE))
      graphics::points(LONGITUD, LATITUDE, pch = 46)
    })
  }
```

## For other functions see package manual
